outline!

### 2016-05-19 paper.tex
paper: update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
paper: updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

Different hardware and different Ceph versions.

>>>>

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in other contexts that may differ by network and hardware capabilities
as well as configuration options and software versions.

To illustrate this we ran the same benchmark that measures expected append
throughput shown in Figure~\ref{fig:vanilla_wr_jewel} on identical hardware
but with a version of long-term support version of Ceph released two years
ago. The result of this benchmark is shown in Figure~\ref{fig:vanilla_wr_firefly}
in which the bytestream interface outperforms the key-value interface by 12\%,
compared to over 100\% in the newer versino of Ceph. Qualatatively, given the
reduced overall throughput achieved in the older version, some developers may
find that incurring the overhead of using the key-value interface is an easy
decision given the reduced complexity of the design space for metadata
management.
